```{r}
library(dplyr)
library(ggplot2)
```

## New Analysis -- Within-Subject
How often do metaphors co-occur above a particular ranking, within-individual
how often are distractors low and things we think are inferrable high

```{r}
all_metas = c("Everybody", "WorkTogether", "Tension", "Disagree", "ManyPeople",
              "GetAlong", "Likes", "Annoyed", "Control", "Feedback")

drop_cols <- function(data) {
  drops <- c("Email.Address", "Start.Date", "End.Date", "IP.Address", "Collector.ID",
             "First.Name", "Last.Name", "Custom.Data.1", "Respondent.ID")
  return(data[, !(names(data) %in% drops)])
}

rename_cols <- function(data) {
  names <- colnames(data)
  for(col in 1:ncol(data)) {
    if(data[1, col] == "She is referring to everybody in the group") {
      names[col] <- "Everybody"
    } else if(data[1, col] == "There is tension between people in the group") {
      names[col] <- "Tension"
    } else if(data[1, col] == "People in the group are working together to solve a problem") {
      names[col] <- "WorkTogether"
    } else if(data[1, col] == "People in the group disagree with one another") {
      names[col] <- "Disagree"
    } else if(data[1, col] == "This group consists of many people") {
      names[col] <- "ManyPeople"
    } else if(data[1, col] == "People in the group generally get along") {
      names[col] <- "GetAlong"
    } else if(data[1, col] == "The speaker likes the people in the group") {
      names[col] <- "Likes"
    } else if(as.character(data[1, col]) == "The speaker is in annoyed with the group") {
      names[col] <- "Annoyed"
    } else if(data[1, col] == "The speaker is in control of the group") {
      names[col] <- "Control"
    } else if(data[1, col] == "The speaker is open to feedback from the group") {
      names[col] <- "Feedback"
    }
  }
  # some bug with "annoyed" not feeding in correctly
  must_be_named <- c("Respondent.ID", "WorkTogether", "Everybody", "Tension", "Disagree",
                     "ManyPeople", "GetAlong", "Likes", "Annoyed", "Control", "Feedback")
  for(i in 1:length(names)) {
    if(!names[i] %in% must_be_named) {
      names[i] <- "Annoyed"
    }
  }
  
  # actually change the column names
  colnames(data) <- names
  data <- data[-1,]
  
  # convert to numerics
  # fuck it nothing is working do it the old fashioned way.
  data$Tension <- as.numeric(as.character(data$Tension))
  data$WorkTogether <- as.numeric(as.character(data$WorkTogether))
  data$Everybody <- as.numeric(as.character(data$Everybody))
  data$Disagree <- as.numeric(as.character(data$Disagree))
  data$ManyPeople <- as.numeric(as.character(data$ManyPeople))
  data$GetAlong <- as.numeric(as.character(data$GetAlong))
  data$Likes <- as.numeric(as.character(data$Likes))
  data$Annoyed <- as.numeric(as.character(data$Annoyed))
  data$Control <- as.numeric(as.character(data$Control))
  data$Feedback <- as.numeric(as.character(data$Feedback))
  
  return(data)
}


drop_incomplete <- function(data) {
  data <- data %>%
    filter(WorkTogether != "" & 
           Feedback != "" & 
           Everybody != "" &
           Tension != "" &
           Disagree != "" &
           ManyPeople != "" &
           GetAlong != "" &
           Likes != "" &
           Annoyed != "" &
           Control != "")
}
```

Read in the data
```{r}
uf_indiv <- read.csv('uf_individuals.csv') %>%
  drop_cols %>%
  rename_cols %>% 
  drop_incomplete
uo_indiv <- read.csv('uo_individuals.csv') %>%
  drop_cols %>%
  rename_cols %>% 
  drop_incomplete
ut_indiv <- read.csv('ut_individuals.csv') %>%
  drop_cols %>%
  rename_cols %>% 
  drop_incomplete
aao_indiv <- read.csv('aao_individuals.csv') %>%
  drop_cols %>%
  rename_cols %>% 
  drop_incomplete
aas_indiv <- read.csv('aas_individuals.csv') %>%
  drop_cols %>%
  rename_cols %>% 
  drop_incomplete
aaop_indiv <- read.csv('aaop_individuals.csv') %>%
  drop_cols %>%
  rename_cols %>% 
  drop_incomplete
eo_indiv <- read.csv('eo_individuals.csv') %>%
  drop_cols %>%
  rename_cols %>% 
  drop_incomplete
ec_indiv <- read.csv('ec_individuals.csv') %>%
  drop_cols %>%
  rename_cols %>% 
  drop_incomplete
es_indiv <- read.csv('es_individuals.csv') %>%
  drop_cols %>%
  rename_cols %>% 
  drop_incomplete
```


Now want to see the average difference between related metaphors. 

i.e. we expect "Tension" and "Disagree" to be somewhat near each other for this case
and we expect Tension and Get Along to be quite far. For the original case we're
interested in the average distance between Tension and Work Together. 
```{r}
compute_diffs <- function(data, meta1, meta2) {
  meta1_scores <- data[[meta1]]
  meta2_scores <- data[[meta2]]
  return(mean(abs(meta1_scores - meta2_scores)))
}
```

Create dissimilarity matrix
get data to look like 
Var1      Var2     value
Tension   Tension    0
GetAlong  Tension    1.42
Disagree  Tension    0.851
...

```{r}

# thanks internet
scale_0_1 <- function(x) { 
  (x-min(x))/(max(x)-min(x))
}


## Go through and populate with metaphors and difference values
create_difference_matrix <- function(data, compare=all_metas) {
  difference_table <- data.frame(
    Meta1 = c(""),
    Meta2 = c(""),
    difference = c(""),
    stringsAsFactors=FALSE
  )
  
  metas = colnames(data)
  metas <- metas[metas %in% compare]
  
  for(metaphor in metas) {
    for(meta in rev(metas)) {
      diff <- compute_diffs(data, meta, metaphor)
      row <- c(metaphor, meta, diff)
      difference_table <- rbind(difference_table, row)  
    }
  }
  
  # difference_matrix$difference <- as.numeric(as.character(difference_matrix$difference))
  difference_table <- difference_table[-1,]
  # there is some problem here with the difference numeric
  difference_table$difference <- as.numeric(as.character(difference_table$difference))
  difference_table$difference <- scale_0_1(difference_table$difference)
  return(difference_table)
}

```

```{r}
plot_diff_matrix_purple <- function(matrix, t) {
  plot_diff_matrix(matrix, "darkorchid4", "aliceblue", "honeydew1", t)
}

plot_diff_matrix_green <- function(matrix, t) {
  plot_diff_matrix(matrix, "darkgreen", "white", "honeydew1", t)
}

plot_diff_matrix_pink <- function(matrix, t) {
  plot_diff_matrix(matrix, "hotpink4", "aliceblue", "mistyrose1", t)
}

plot_diff_matrix_blue <- function(matrix, t="") {
  plot_diff_matrix(matrix, "royalblue4", "aliceblue", "slategray1", title=t)
}

plot_diff_matrix <- function(matrix, low_col, high_col, mid_col, title) {
  ggplot(data=matrix, aes(x=Meta1, y=Meta2, fill=difference)) + 
  geom_tile(color="white") +
  scale_fill_gradient2(low=low_col, high=high_col, mid=mid_col,
                       midpoint=0.5, space="Lab") +
  theme_minimal() +
  coord_fixed() +
  theme_bw() +
  theme(axis.text.x=element_text(angle=90),
      axis.ticks=element_blank(),
      axis.line=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_line(color='#eeeeee')) +
    ggtitle(title)
}
```


Actually plot them for each one
## "Unpolite"
```{r}
unpolite_metas <- c("WorkTogether", "Tension", "Disagree", "GetAlong", "Annoyed")
```

```{r}
u_orig_diff_plot <- create_difference_matrix(uo_indiv) %>%
  plot_diff_matrix_blue("Original")

u_orig_diff_plot
```

```{r}
u_forced_diff_plot <- create_difference_matrix(uf_indiv) %>%
  plot_diff_matrix_blue("Forced")

u_forced_diff_plot
```

```{r}
u_together_diff_plot <- create_difference_matrix(ut_indiv) %>%
  plot_diff_matrix_blue("Together")

u_together_diff_plot
```

## "Audience"
```{r}
audience_metas <- c("Everybody", "ManyPeople", "GetAlong", "Control", "Feedback", "Likes")
```

```{r}
plot_diff_matrix_blue(create_difference_matrix(aao_indiv), "Original")
```

```{r}
plot_diff_matrix_blue(create_difference_matrix(aas_indiv), "Small")
```

```{r}
plot_diff_matrix_blue(create_difference_matrix(aaop_indiv), "Open")
```

## "Entity"
```{r}
entity_metas <- c("Tension", "Disagree", "Likes", "Annoyed", "Control")
```

```{r}
plot_diff_matrix_blue(create_difference_matrix(eo_indiv), "Original")
```

```{r}
plot_diff_matrix_blue(create_difference_matrix(ec_indiv), "Chest")
```

```{r}
plot_diff_matrix_blue(create_difference_matrix(es_indiv), "Separate")
```





## Average Mean Ranking
```{r}
get_avg_ranking <- function(data) {
  ranked <- data.frame("metaphor", "avg_ranking", stringsAsFactors=FALSE)
  ranked <- rbind(ranked, c("WorkTogether", as.numeric(as.character(mean(data$WorkTogether)))))
  ranked <- rbind(ranked, c("Everybody", mean(data$Everybody)))
  ranked <- rbind(ranked, c("Tension", mean(data$Tension)))
  ranked <- rbind(ranked, c("Disagree", mean(data$Disagree)))
  ranked <- rbind(ranked, c("ManyPeople", mean(data$ManyPeople)))
  ranked <- rbind(ranked, c("GetAlong", mean(data$GetAlong)))
  ranked <- rbind(ranked, c("Likes", mean(data$Likes)))
  ranked <- rbind(ranked, c("Annoyed", mean(data$Annoyed)))
  ranked <- rbind(ranked, c("Control", mean(data$Control)))
  ranked <- rbind(ranked, c("Feedback", mean(data$Feedback)))
  return(ranked[-1,])
}

uo_indiv_avg_rank_plot <- ggplot(get_avg_ranking(uo_indiv), aes(x=X.metaphor., y=X.avg_ranking.)) + 
    geom_bar(stat="identity", position="dodge") 
uo_indiv_avg_rank_plot

uf_indiv_avg_rank_plot <- ggplot(get_avg_ranking(uf_indiv), aes(x=X.metaphor., y=X.avg_ranking.)) + 
    geom_bar(stat="identity", position="dodge") 
uf_indiv_avg_rank_plot

ut_indiv_avg_rank_plot <- ggplot(get_avg_ranking(ut_indiv), aes(x=X.metaphor., y=X.avg_ranking.)) + 
    geom_bar(stat="identity", position="dodge") 
ut_indiv_avg_rank_plot


```