---
title: "IVA2019 Analysis"
author: "CSaund"
date: "2/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Load these bad larrys
Annoyingly can't create dynamically named variables in R AFAIK, so manual
```{r}
condition_names <- c('aao', 'aas', 'aaop', 'eo','ec','es','uo','uf','ut')

aao <- read.csv('AAO_copy.csv')
aao_scores <- aao$Score
aao_sd <- sd(aao_scores)

aas <- read.csv('AAS_copy.csv')
aas_scores <- aas$Score
aas_sd <- sd(aas_scores)

aaop <- read.csv('AAOP_copy.csv')
aaop_scores <- aaop$Score
aaop_sd <- sd(aaop_scores)

eo <- read.csv('EO_copy.csv')
eo_scores <- eo$Score
eo_sd <- sd(eo_scores)

ec <- read.csv('EC_copy.csv')
ec_scores <- ec$Score
ec_sd <- sd(ec_scores)

es <- read.csv('ES_copy.csv')
es_scores <- es$Score
es_sd <- sd(es_scores)

uo <- read.csv('UO_copy.csv')
uo_scores <- uo$Score
uo_sd <- sd(uo_scores)

ut <- read.csv('UT_copy.csv')
ut_scores <- ut$Score
ut_sd <- sd(ut_scores)

uf <- read.csv('UF_copy.csv')
uf_scores <- uf$Score
uf_sd <- sd(uf_scores)

```

Are within-gesture variances significantly different? 
AAO:AAOP No
F = 0.71733, num df = 9, denom df = 9, p-value = 0.6286
AAO: AAS No
F = 1.0886, num df = 9, denom df = 9, p-value = 0.9014
AAS:AAOP No
F = 0.65892, num df = 9, denom df = 9, p-value = 0.5442


EO:EC No
F = 0.43712, num df = 9, denom df = 9, p-value = 0.2336
EO:ES Yes
F = 0.18854, num df = 9, denom df = 9, p-value = 0.02061
ES:EC No
F = 2.3184, num df = 9, denom df = 9, p-value = 0.2263

UO:UF No
F = 1.4853, num df = 9, denom df = 9, p-value = 0.565
UO:UT No
F = 1.3844, num df = 9, denom df = 9, p-value = 0.6358
UF:UT No
F = 1.0729, num df = 9, denom df = 9, p-value = 0.9182

```{}
var.test(aao_scores, aaop_scores, alternative = "two.sided")
var.test(aao_scores, aas_scores, alternative = "two.sided")
var.test(aas_scores, aaop_scores, alternative = "two.sided")

var.test(eo_scores, ec_scores, alternative = "two.sided")
var.test(eo_scores, es_scores, alternative = "two.sided")
var.test(es_scores, ec_scores, alternative = "two.sided")

var.test(uo_scores, uf_scores, alternative = "two.sided")
var.test(uo_scores, ut_scores, alternative = "two.sided")
var.test(ut_scores, uf_scores, alternative = "two.sided")

```

Human-interpretable results:
Largely, the variance within gesture conditions was not statistically significant, 
disproving our hypothesis that more complex metaphors are more difficult to interpret. 

Now let's bucket the responses and see if our results change. 

First step, collapse responses into metaphor-y responses. 
1. (Force is conflict) Combine rows for "There is tension between people in the group" and "People in the group disagree with one another"
2. (Physical closeness is ideological closeness) Combine "People in this group generally get along" and "People in the group are working together to solve a problem"
3. (Abstract ideas have concrete properties (size)) "She is referring to everybody in the group" and "This group consists of many people"
4. (Open is accessible) "The speaker likes the people in the group" and "The speaker is open to feedback from the group"
5. (Being in control is being above) "The speaker is annoyed with the group" and "The speaker is in control of the group"

This means we're gonna have to calculate our own scores
```{}
get_scores <- function(data) {
  scores <- c()
  for(row in 1:nrow(data)) {
    total_score = 0
    for(col in 2:11) {
      total_score = total_score + data[row,col] * (12 - col)
    }
    scores[row] <- (total_score / data[row,12])
  }
  return(scores)
}
```
This function does just that -- calculates the scores for each metaphor in a data set. 

Now let's make copies of our data with our bucketed scores
```{}
append_scores <- function(data) {
  scores <- get_scores(data)
  data$new_score=scores
  return(data)
}
```


Great, now that we can actually calculate our own scores and add them to our data, let's add a "group"
column that actually tells us what the metaphors were in reference to. 
```{}
group_by_metaphor <- function(data) {
  data$group <- ""
  for(row in 1:nrow(data)) {
    if (data$Answer.Choices[row] == "People in the group are working together to solve a problem" || 
        data$Answer.Choices[row] == "People in the group generally get along") {
      data$group[row] <- "closeness"
    } else if (data$Answer.Choices[row] == "There is tension between people in the group" || 
               data$Answer.Choices[row] == "People in the group disagree with one another") {
      data$group[row] <- "conflict"
    } else if (data$Answer.Choices[row] == "She is referring to everybody in the group" || 
               data$Answer.Choices[row] == "This group consists of many people") {
      data$group[row] <- "size"
    } else if (data$Answer.Choices[row] == "The speaker likes the people in the group" || 
               data$Answer.Choices[row] == "The speaker is open to feedback from the group") {
      data$group[row] <- "open"
    } else if (data$Answer.Choices[row] == "The speaker is in annoyed with the group" || 
               data$Answer.Choices[row] == "The speaker is in control of the group") {
      data$group[row] <- "control"
    } else {
      # for some reason it's not recognizing the annoyed case, so let's throw it in the else
      # cause that seems safe.
      data$group[row] <- "control"
    }
  }
  return(data)
}
```


Sweet, now that we have groups, we can combine data by group in order to create our new scores.
```{}
bucket_by_group <- function(data) {
  return (aggregate(list(X1=data$X1, 
                 X2=data$X2,
                 X3=data$X3,
                 X4=data$X4,
                 X5=data$X5,
                 X6=data$X6,
                 X7=data$X7,
                 X8=data$X8,
                 X9=data$X9,
                 X10=data$X10,
                 Total=data$Total), 
             by=list(Group=data$group), 
             FUN=sum))
}
```
Sweet, now instead of dealing with survey statements we're dealing with semantic meaning. 

Let's get those scores going
```{}
# Just kidding, we already have the score calculator, just run this! 
# append_scores(bucketed_data)

```

Just to be clear, this is what we're doing start to finish to get a nice and shiny 
bucketed dataset with new scores we can then compare variances of, based on the semantic
meanings and not the actual survey statements
```{}
transform_data <- function(data) {
  transformed_data <- data %>%
    group_by_metaphor() %>%
    bucket_by_group() %>%
    append_scores()
}
``` 







